Some examples in extended logic counting classes

### 2016-09-16 QSO/logics.tex
15 sep

To formally characterize its semantics we define the partial function $\zeta_{\varphi,\alpha}:2^{A^k} \to (A^{\ell}\times\nat)$ for each $\varphi$ and $\alpha$ as follows. Let $\A$ be a structure. For $R = \emptyset$, it holds that $\zeta_{\varphi,\alpha}[\emptyset] = \sem{\alpha\mid_{\pi(\bar{u})\to 0}}$. For each $R \subseteq A^k$ such that $T_{\varphi}(R) \neq R$, let $\beta$ be a virtual $\qfo$ formula such that $\sem{\beta}(\A,v) = \zeta_{\varphi,\alpha}[R](v)$ for each first order assignment $v$, and it holds that $\zeta_{\varphi,\alpha}[T_{\varphi}(R)] = \sem{\alpha\mid_{\pi\to\beta}}$.

>>>>

To formally characterize its semantics we define the partial function $\zeta_{\varphi,\alpha}:2^{A^k} \to (A^{\ell}\times\nat)$ for each $\varphi$ and $\alpha$ as follows. Let $\A$ be a structure. For $R = \emptyset$, we define $\zeta_{\varphi,\alpha}[\emptyset] = \sem{\alpha\mid_{\pi(\bar{u})\to 0}}$. For each $R \subseteq A^k$ such that $T_{\varphi}(R) \neq R$, let $\beta$ be a virtual $\qfo$ formula with $\ell$ open variables such that $\sem{\beta}(\A,v) = \zeta_{\varphi,\alpha}[R](v)$ for each first order assignment $v$, and we define $\zeta_{\varphi,\alpha}[T_{\varphi}(R)] = \sem{\alpha\mid_{\pi(\bar{u})\to\beta(\bar{u})}}$.
